### 2014-02-12 classicthesis/Chapters/Introduction.tex
laatste puntjes netjes gemaakt voordat Sander de draft kreeg

\begin{description}
\item[Part II ]{introduces the reader to the basic principles and recent work in the fields of Learning-to-Rank.}
\item[Part III ]{sketches the performance of existing Learning-to-Rank methods on several benchmark datasets.}
\item[Part IV ]{concisely describes existing work in the field of parallel machine learning and parallel Learning-to-Rank.}
\item[Part V ]{describes implementation details of the Learning-to-Rank algorithms in the Hadoop framework.}
\item[Part VI ]{presents and discusses speed-up results for the implemented Learning-to-Rank methods.}
\item[Part VII ]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\end{description}

>>>>

\begin{description}
\item[Part II: Background ]{introduces the reader to the basic principles and recent work in the fields of Learning-to-Rank.}
\item[Part III: Related Work]{concisely describes existing work in the field of parallel machine learning and parallel Learning-to-Rank.}
\item[Part IV: Benchmark Results]{sketches the performance of existing Learning-to-Rank methods on several benchmark datasets and describes the selection of Learning-to-Rank methods for the parallelization experiments.}
\item[Part V: Selected Learning-to-Rank Methods]{describes the algorithms and details of the selected Learning-to-Rank methods.}
\item[Part VI: Implementation]{describes implementation details of the Learning-to-Rank algorithms in the Hadoop framework.}
\item[Part VII: Results \& Discussion]{presents and discusses speed-up results for the implemented Learning-to-Rank methods.}
\item[Part VIII: Conclusion]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\end{description}
